---
title: "HW 10"
author: "Daniel Yoon"
date: "2024-04-25"
output:
  pdf_document: default
  html_document: default
---
HW 10
Daniel Yoon
UT EID: dey246


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Read the data
redline <- read.csv("redlining.csv")

#1) What question are you trying to answer?
lm_redline <- lm(policies ~ minority + fire + age + income, data=redline)

summary(lm_redline)

confidence_intervals <- confint(lm_redline)

print(confidence_intervals)
```
I used linear regression model to asnwer whether there is an association between the number of FAIR policies and the racial/ethic composition of a ZIP code, and I used p-values as my evidence. According to the summary of linear regression model, minority and fire have significant association with the number of FAIR policies because they had value of 0.00611 and 0.01833. However, age and income does not seem to have significant association because they had value of 0.14323 and 0.67863, which means that they failed to reject the null hypothesis. the 95% confidence interval of minority is 0.0025 to 0.0142, interval of fire is 0.0039 to 0.0396, interval of age is -0.002 to 0.0132,and interval of income is -0.0935 to 0.0616. In conclusion, minority and fire impacts people to take the FAIR policies rather than private market.
```{r}
# Problem 2
# Part A
library(dplyr)
library(ggplot2)

groceries <- read.csv("groceries.csv")

# Aggregate data to calculate average price per store
average_prices <- groceries %>%
  group_by(Store) %>%
  summarize(Avg_Price = mean(Price))

# Plot the bar graph with coord_flip
ggplot(average_prices, aes(x = Store, y = Avg_Price)) +
  geom_bar(stat = "identity", fill = "blue") +
  coord_flip() +
  labs(title = "Average Price of Products Sold at Different Stores",
       x = "Store",
       y = "Average Price ($)",
       caption = "Whole Foods has the highest average price of products sold.")

  
  theme_minimal()


```


```{r}
# Part B
# Load the required libraries
library(dplyr)
library(ggplot2)

# Read the dataset
groceries <- read.csv("groceries.csv")

# Wrangle the data to count the number of stores selling each product
product_counts <- groceries %>%
  group_by(Product) %>%
  summarize(Num_Stores = n_distinct(Store))

# Plot the bar graph
ggplot(product_counts, aes(x = Num_Stores, y = Product)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Number of Stores Selling Each Product",
       x = "Number of Stores",
       y = "Product") +
  theme_minimal()



```


```{r}
#Part C

# Fit a linear regression model
# Fit a regression model for Price versus Product and Type of store
model <- lm(Price ~ Product + Type, data = groceries)


# Get summary of the regression model
summary_model <- summary(model)

# Extract coefficient estimate and standard error for TypeConvenience
coefficient <- coef(model)["TypeConvenience"]
std_error <- summary_model$coefficients["TypeConvenience", "Std. Error"]

# Calculate the degrees of freedom
n <- length(your_data_frame$Price)
p <- length(coef(model))
df <- n - p

# Calculate the t-statistic for a 95% confidence interval
t_value <- qt(0.975, df)

# Calculate the margin of error
margin_error <- t_value * std_error

# Calculate the confidence interval bounds
lower_bound <- coefficient - margin_error
upper_bound <- coefficient + margin_error

# Round the bounds to two decimal places
lower_bound <- round(lower_bound, 2)
upper_bound <- round(upper_bound, 2)

# Print the confidence interval
cat("The 95% confidence interval for the difference in prices between convenience stores and ordinary grocery stores is between $", lower_bound, "and $", upper_bound, ".", sep = "")







```

```{r}
# Fit a regression model for Price versus Product and Store
model_store <- lm(Price ~ Product + Store, data = groceries)

# Get summary of the regression model
summary_model_store <- summary(model_store)

# Extract coefficients for each store
coefficients_store <- summary_model_store$coefficients["Store", "Estimate"]

# Find the two stores with the lowest and highest prices
lowest_prices <- head(sort(coefficients_store), 2)
highest_prices <- tail(sort(coefficients_store), 2)

# Print the results
cat("The two stores charging the lowest prices are:", names(lowest_prices), "\n")
cat("The two stores charging the highest prices are:", names(highest_prices), "\n")


```

